Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-25 stp/paper_aaai/main.tex
updated info Natalia

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission 1228)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Submission 1228}
\maketitle
\begin{abstract}
%% REWRITTEN:

@@

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems such as:
naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
content. %, for example, startDate versus endDate for the Event class.
Also, there may be a considerable number of attributes which have no 
corresponding property in the ontology (accidentaly or deliberately).
%\ddg{CHECK!}

>>>>

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Diego De Una , Natalia Rummele, Graeme Gange, Peter Schachte and Peter J. Stuckey)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Diego De U\~na$^1$ , Natalia R\"ummele$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,3}$\\
$^1$Department of Computing and Information Systems --- The University of Melbourne\\
$^2$Siemens, Germany ~~~~~
$^3$Data61, CSIRO, Melbourne, Australia\\
d.deunagomez@student.unimelb.edu.au, nataliia.ruemmele@siemens.com\\ \{gkgange,schachte,pstuckey\}@unimelb.edu.au
}

\maketitle
\begin{abstract}
%% REWRITTEN:

@@

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems such as:
naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
content. %, for example, startDate versus endDate for the Event class.
Also, there may be a considerable number of attributes which have no 
corresponding property in the ontology (accidentally or deliberately).
%\ddg{CHECK!}
